Evaluating Modern vs. Older Buildings: Detailed Analysis on the Apartment Building Evaluation 2023

### 2024-01-23 Output/Paper/BuildingScoreAnalyze-2023.qmd
Update on llm and peer review

## create a bar chart of evaluation standard vs. percentage with help of Chatgpt
ggplot(data_frequency, aes(x = Category, y = Value, fill = as.factor(Year))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_brewer(palette = "Set1") + 
  labs(x = "Category", y = "Percentage", title = "Percentage for buildings of achieving a full Mark") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

@@

Before drawing conclusions, let's revisit Fig 1. Noticeable outliers[^1], such as a building built in 1954 at 5 A Jasper Ave with a score of 17 out of 100, do bring the overall average down. Yet, denying the average score graph entirely would be hasty. A closer inspection of Fig 1 reveals that, excluding outliers, the score range for the 20th century (approximately 60 to 100) is still broader than that of the 21st century (about 82 to 100). Even with a 90% quantile or percentile adjustment, the pattern of increasing scores is unlikely to change significantly due to the dataset's size and score range.

@@

>>>>

## create a bar chart of evaluation standard vs. percentage with help of Chatgpt
ggplot(data_frequency, aes(x = Category, y = Value, fill = as.factor(Year))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_brewer(palette = "Set1") + 
  labs(x = "Category", y = "Percentage", title = "Percentage for buildings of achieving a full Mark") +
  scale_fill_manual(values = c("1950" = "pink", "2000" = "blue")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

\newpage

@@

Before drawing conclusions, let's revisit Fig 1. Noticeable outliers[^1], such as a building built in 1954 at 5 A Jasper Ave with a score of 17 out of 100, do bring the overall average down. Yet, denying the average score graph entirely would be hasty. A closer inspection of Fig 1 reveals that, excluding outliers, the score range for the 20th century (approximately 60 to 100) is still broader than that of the 21st century (about 82 to 100). Even with a 90% quantile or percentile adjustment, the pattern of increasing scores is unlikely to change significantly due to the dataset's size and score range [^2].

@@

[^2]:**Note: After Peer Review, a friend commented my paper and said that outliers are serious issue and suggest that I take care of it. I redid my codes and removed 1% each side of my data on column score and I found that my conclusion stayed the same. The graph is still having a trend I talked about above. Thanks to @ zxc0707.
